BlogForever Crawler: Techniques and Algorithms\\to Harvest Modern Weblogs

### 2014-01-15 tex/1-intro.tex

\begin{itemize}
  \item We present a new generic algorithm to build extraction from a set of pages and target content. We then derive an optimized reformulation tied to a particular string similarity and show that this reformulated algorithm has a linear time complexity.
  \item We show how to use this algorithm to extract blog articles, and how it can be adapted to extract authors, publication dates and comments.
  \item We present the overall crawler architecture and the specific components we implemented to efficiently traverse blogs. We explain how our design allows for both modularity and scalability.
  \item We show how we make use of a complete web browser to render JavaScript powered web pages before processing them. This step allows our crawler to effectively harvest blogs built with modern technology, such as the increasingly popular third-party commenting systems.
  \item We present and analyze performance results of our algorithm in terms of extraction success rates and execution time. A comparison is made with three state-of-the-art article extraction algorithms.
\end{itemize}

>>>>

\begin{itemize}
  \item We present a new algorithm to build extraction rules from web feeds. We then derive an optimized reformulation tied to a particular string similarity and show that this reformulated algorithm has a linear time complexity.
  \item We show how to use this algorithm for blog article extraction, and how it can be adapted to authors, publication dates and comments.
  \item We present the overall crawler architecture and the specific components we implemented to efficiently traverse blogs. We explain how our design allows for both modularity and scalability.
  \item We show how we make use of a complete web browser to render JavaScript powered web pages before processing them. This step allows our crawler to effectively harvest blogs built with modern technology, such as the increasingly popular third-party commenting systems.
  \item We present and analyze performance results of our algorithm in terms of extraction success rates and execution time. A comparison is made with three state-of-the-art article extraction algorithms.
\end{itemize}
